---
title: "Skills Test 3"
author: "Sonia"
date: "4/4/2022"
output: 
  html_document:
    code_folding: hide
---
Libraries to load before you start:
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(janitor)
library(modelr)
library(easystats)
library(broom)
theme_set(theme_minimal())
```



1. Load and clean FacultySalaries_1995.csv. Then graph Salary vs Rank facteted by Tier.

```{r message=FALSE, warning=FALSE}

#loading data
df<- read_csv("./FacultySalaries_1995.csv")
#tidying
#split into several data frames by faculty ranks for convenience
Assist<- df %>%
  select(FedID, UnivName, State, Tier, AvgAssistProfSalary, AvgAssistProfComp,
         NumAssistProfs, NumInstructors, NumFacultyAll) 

Assoc<- df %>%
  select(FedID, UnivName, State, Tier, AvgAssocProfSalary, AvgAssocProfComp,
         NumAssocProfs, NumInstructors, NumFacultyAll) 

Full<- df %>%
  select(FedID, UnivName, State, Tier, AvgFullProfSalary, AvgFullProfComp,
         NumFullProfs, NumInstructors, NumFacultyAll) 

Assist<- Assist %>% 
  mutate(Rank="Assist", Salary=AvgAssistProfSalary, Comp=AvgAssistProfComp) %>% 
  select(-c(AvgAssistProfSalary, AvgAssistProfComp, NumAssistProfs))

Assoc<- Assoc %>% 
  mutate(Rank="Assoc", Salary=AvgAssocProfSalary, Comp=AvgAssocProfComp) %>% 
  select(-c(AvgAssocProfSalary, AvgAssocProfComp, NumAssocProfs))

Full<- Full %>% 
  mutate(Rank="Full", Salary=AvgFullProfSalary, Comp=AvgFullProfComp) %>% 
  select(-c(AvgFullProfSalary, AvgFullProfComp, NumFullProfs))

#joining
full <- full_join(Assist, Assoc) %>% 
  full_join(Full)

#Visualize!
full %>% 
  filter(!Tier=='VIIB') %>% 
  ggplot(aes(x=Rank, y=Salary, fill=Rank))+
  geom_boxplot() +
  facet_wrap(~Tier)

```


2. Build an ANOVA model and display the summary output in your report.
```{r}
mod<- aov(data=full,
            formula=Salary ~ State + Rank + Tier)

tidy(mod)

```

3. Load and Tidy “Juniper_Oils.csv”

```{r message=FALSE, warning=FALSE}
#Load in the data
df<- read_csv("./Juniper_Oils.csv")
#Time to tidy
chem<- df %>%
  pivot_longer(cols=c("alpha-pinene","para-cymene","alpha-terpineol","cedr-9-ene","alpha-cedrene","beta-cedrene","cis-thujopsene","alpha-himachalene","beta-chamigrene","cuparene","compound 1","alpha-chamigrene","widdrol","cedrol","beta-acorenol","alpha-acorenol","gamma-eudesmol","beta-eudesmol","alpha-eudesmol","cedr-8-en-13-ol","cedr-8-en-15-ol","compound 2","thujopsenal"),
               names_to="ChemicalID",
               values_to="Concentrations")

```

4. Graph the concentration of the compounds by years since burn, faceted by chemical ids.

```{r message=FALSE, warning=FALSE}
chem %>% 
  ggplot(aes(x=YearsSinceBurn, y=Concentrations))+
  geom_smooth() +
  facet_wrap(~ChemicalID, scales = "free_y")
```

5.  Use a generalized linear model to find which chemicals show concentrations that are significantly (significant, as in P < 0.05) affected by “Years Since Burn”.

```{r}
#mod2<- glm(data=chem,
           #formula= ChemicalID ~ Concentrations + YearsSinceBurn)

#tidy(mod2) %>% 
  #filter(p.value<0.05)
```




